ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-05-06 paper.tex
Edited prev work

Making a mobile device that can detect objects and guide a PwVI in real-time and using on-board processing power has become much more feasible in recent years, thanks to improvements to mobile computing power and image processing methods.
Early attempts to solve this guidance problem made use of special markers or barcodes, encoded with object or environmental information, and a smartphone that can efficiently scan the environment for these simple patterns~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}. 
The device then uses some feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
Improvements to feature detectors and deep networks have made it more viable~\cite{redmon2016you,huang2017speed} to replace the markers with real objects, while providing the same guidance functionality.
The SIFT and SURF-based systems in~\cite{schauerte2012assistive} is an example of a markerless system.
An alternative detection approach proposed in~\cite{bigham2010vizwiz}, and commercialised in the `Be My Eyes' app~\cite{bemyeyes2019}, requires the user to send a photo of their environment and target object to a Mechanical Turk worker or volunteer that then sends the position of the requested object within the picture back to the user.

The issue with the marker-based approach is that it requires a significant amount of effort to place and maintain markers around an environment.
This problem is remedied in the markerless systems.
However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves first before any guidance can be provided. 
The human-based systems from~\cite{bigham2010vizwiz,bemyeyes2019} can leverage a human's understanding of the environment to help guide a person to the correct area, but the drawback here is that there is a significant lag time and a significant reliance on a good internet connection and remote worker being available. 
Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing a controller that provides the user with instructions on where to point the device to find an out of view object and we proved that this is a viable method to search for an object. 
However, this work relied upon physical barcodes, encoded with object information, to simulate real objects.
In this work, we are replacing the barcodes with real objects, thereby closing the object detection and guidance loop.

Object detectors can be divided into two main categories that use single-stage and 2-stage methods.  
The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects. 
They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements~\cite{liu2018deeplf}.
On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
This leads to model that uses much less memory, but again with a small drop in accuracy.

>>>>

Making a mobile device that can detect objects and guide a PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing power and image processing methods.
Early attempts to solve this guidance problem made use of special markers encoded with object or environmental information, and a smartphone that can scan the environment for these simple patterns~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}. 
The device uses some feedback mode (e.g.\ voice, Braille) to read out the embedded information or guide the user towards the markers. 
Improvements to feature detectors and deep networks have made it more viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects while providing the same guidance functionality.
The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.
An alternative detection approach proposed in~\cite{bigham2010vizwiz}, and commercialised in the `Be My Eyes' app~\cite{bemyeyes2019}, requires the user to send the desired object and a photo of their environment to a Mechanical Turk worker or volunteer that sends the position of the requested object within the picture back to the user.

The issue with the marker-based approach is that it requires a significant amount of effort to place and maintain markers around an environment, which is remedied by markerless systems.
However, both of these approaches are passive in their guidance approach and rely on the user placing the desired marker/object within the camera's view by themselves first before any guidance is provided. 
The systems in~\cite{bigham2010vizwiz,bemyeyes2019} can leverage a human's understanding of the environment to help guide a person to the correct area, but the drawback here is that there is significant lag, and a reliance on a good internet connection and remote worker being available. 
Our previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that provides the user with pointing instructions to find an out of view object and proved that this is a viable method to search for an object. 
However, this work relied on physical barcodes encoded with object information to simulate real objects.
In this work, we are replacing the barcodes with real objects, thereby providing a complete object detection and guidance pipeline.

Object detectors can be divided into two main categories: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
Between the 2 types, there is a speed-accuracy tradeoff, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
On the other hand, single-stage models, such as SSD, YOLO and MobileNet~\cite{liu2016ssd,redmon2018yolo,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models. 
%MobileNet~\cite{howard2017mobilenet} in particular is a 2-stage network designed specifically for mobile platforms with moderate precision levels, but can reach around 10 frames per second on a mobile platform.
%The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects. 
%They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements~\cite{liu2018deeplf}.
%On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
%These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
%Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
%There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
%MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
%This leads to model that uses much less memory, but again with a small drop in accuracy.
